%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\usepackage{fontawesome5}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\collegeItem}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small } \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\texthash}{\#}
\newcommand{\percent}{\%}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Prem Kumar} \\ \vspace{1pt}
    Lakhisarai, Bihar, India 811311 \\ \vspace{1pt}
    \href{tel:919470678079}{\color{MidnightBlue} \raisebox{-0.2\height}\faPhone\
    \underline {+91 9470678079}} ~ \href{mailto:premraj259@outlook.com}{\color{MidnightBlue} \raisebox{-0.2\height}\faEnvelope\  \underline{premraj259@outlook.com}} ~ 
    \href{https://linkedin.com/in/prem-kr/}{\color{MidnightBlue} \raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/prem-kr}}  ~
    \href{https://github.com/}{\color{MidnightBlue} \raisebox{-0.2\height}\faGithub\ \underline{github.com/rpremofficial}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Bhagalpur}{Nov 2020 -- July 2024}
      {Bachelor of Technology in Computer Science and Engineering}{Bhagalpur, Bihar}
  \resumeSubHeadingListEnd
  \collegeItemsistStart
  \collegeItem{\textbf{Cgpa:} 7.38 (absolute)}
  \collegeItem{\textbf{Relevant Coursework:} Data Structures, Algorithms, OOPS, DBMS, Operating System, AI/ML, Software Engineering}
  \collegeItemsisEnd
\vspace{-2pt}
  

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Algorithms
%                 \item Operating System
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Computer Networking
%                 \item Systems Design
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Internship}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Glocybs (cybersecurity startup)}{May 2022 -- July 2022}
      {Full Stack Developer Intern}{Noida, UP}
      \resumeItemListStart
        \resumeItem{Contributed in \textbf{development of app and website} having features like account management, subscription notification, and 24/7 customer support (AI Chat-bot) to address cyberattack \& bugs/issues.}
        \resumeItem{Acquired expertise in \textbf{building \& hosting fully functional website} and utilized Firebase \& MongoDB for developing \& testing. Collaborated regularly using Git \& GitHub for the duration of 2 months.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{\href{https://github.com/TnP-Cell/Student-Portal}{\color{MidnightBlue} \underline{Student and Admin portal}}} $|$ \emph{ReactJS, Node.Js, JavaScript, CSS, PostgreSQL} $|$ \emph{\color{MidnightBlue} \href{https://github.com/TnP-Cell/Student-Portal}\faGithub{}}}{May 2023 - July 2023}
          \resumeItemListStart
            \resumeItem{Designed and Developed a \textbf{one stop platform} from scratch to simplify the process of multiple administration and 1000+ students in college.}
            \resumeItem{Student portal: Having features like \textbf{Dashboard, Fee payment, Course registration, result checking} and access to  various \textbf{documents/forms.} As a result we reduced the process time from 3 days to 1/2 minutes.}
            \resumeItem{Admin portal: Contains \textbf{multiple roles} having features like \textbf{managing fee, approval for result/registration, generating bulk receipts, and basic automations} (like late fines, summary creation, reminders).}
        \resumeItemListEnd
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{\href{https://tnp.iiitbh.ac.in/}{\color{MidnightBlue} \underline{Placement Portal}}} $|$ \emph{JavaScript, Node.js, MongoDB} $|$ \emph{\color{MidnightBlue} \href{https://github.com/TnP-Cell/Frontend-TnP}\faGithub{}}}{Apr 2022 - Jun 2022}
          \resumeItemListStart
            \resumeItem{Developed a single window portal for College Training and Placement Cell with \textbf{2,000+ active users} for Internship and Placement management.}
            \resumeItem{Created a \textbf{dashboard} for students, recruiters, and an admin center for TPC officers to streamline news publishing, event conducting, and document management, reducing management time by 30{\percent}}
            \resumeItem{Implemented features such as gallery, past recruiters marquee, statistics of 3 years, with a \textbf{modern user interface.}}
        \resumeItemListEnd
        \vspace{-13pt}
        \resumeProjectHeading
          {\textbf{\href{https://otarea.in/}{\color{MidnightBlue} \underline{Otarea.in}}} $|$ \emph{HTML, CSS, JavaScript, Azure} $|$ \emph{\color{MidnightBlue} \href{https://github.com/Otarea/Otarea_old}\faGithub{}}}{Oct 2021 - Feb 2022}
          \resumeItemListStart
            \resumeItem{Building a \textbf{business-oriented platform} for design product/services with education and support sections.}
            \resumeItem{Created a \textbf{portfolio} of 100+ editable design templates with an education section having documentations and videos.}
            \resumeItem{Integrated collaborative features such as \textbf{blogs, digital whiteboard, and a chat-bot} using JavaScript and an API.}
        \resumeItemListEnd 
        % \vspace{-13pt}
        % \resumeProjectHeading
        %   {\textbf{One Stop Platform for Entrepreneurs} $|$ \emph{ React.JS, AWS, MySQL, Firebase}}{Feb 2022 - Apr 2022}
        %   \resumeItemListStart
        %     \resumeItem{Developed one stop platform providing various features to support entrepreneurs  with ideation, registration, incubation, mentorship, funding, and marketing.}
        %     \resumeItem{As a \textbf{team lead} (of 6 people)  in Smart India Hackathon 2022 played key role in ideation of project, web development, and solution presentation.}
        % \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-13pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming languages}{: C++, JavaScript, CSS, HTML} \\
     \textbf{Web development}{: React.JS, Node.js, Bootstrap} \\
     \textbf{UI/UX design}{: Figma, prototyping} \\
     \textbf{Technologies/Platforms}{: Azure, Firebase, MongoDB, Git, Github} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Achievements}
    \resumeSubHeadingListStart
        % \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
            \resumeItemListStart
                \resumeItem{\textbf{Got project offer from Bhagalpur Police:} Will be working to simplify process and solve a real world problem.}
                \resumeItem{\textbf{Won Smart India Internal Hackathon:} Led the team and finished in top 5 out of 25 participating teams.}
                \resumeItem{\textbf{Solved 600+ Coding Questions:} Demonstrated proficiency in coding by solving over 300+ questions on 
                {{\href{https://leetcode.com/rpremofficial/}{\color{MidnightBlue} \underline{\textbf{LeetCode}}}}}, 200+ on 
                {{\href{https://codeforces.com/profile/kr.prem}{\color{MidnightBlue} \underline{\textbf{Codeforces}}}}}
                and rest on others. Participated regularly in coding contests on various online platforms.}
                \resumeItem{\textbf{Achieved 3 Star on {{\href{https://www.codechef.com/users/rpremofficial}{\color{MidnightBlue} \underline{CodeChef:}}}}} with best global rank 157 and total rating of 1665 points.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-13pt}


\section{Extracurricular / Position of responsibility}
    \resumeSubHeadingListStart
        % \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
            \resumeItemListStart
                \resumeItem{\textbf{Led design/branding team and Managed business/tech events:} in Enyugma, techno-cultural fest 2022.}
                \resumeItem{\textbf{Training \& Placement Coordinators:} Worked in the College Placement Division, hosted 20+ events related to technical and personal skills, building strong connections between 200+ recruiters and 1200+ students/alumni.}
                \vspace{2pt}
                \resumeItem{\textbf{Elected as Head of Design Team:} while leading design team of the college honed my UI and UX skills, Designed and improved existing design of over 25 websites and apps. Enhanced the quality and appeal of the college events/clubs.}
                \vspace{2pt}
                \resumeItem{\textbf{Appointed as Entrepreneurship Club Coordinator:} Led a team of \textbf{30+ student entrepreneurs}, utilizing leadership, collaboration, and analytic skills. Gained hands-on experience in developing user-centric software solutions.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
